A holomorphic approach to membranes and fivebranes

### 2022-07-07 fivebranes/kr.tex
merge

\begin{lem}
We have
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
\eeqn
\end{lem}

Before moving on, we point out that in the formula for $R$ if we specialize $t_1=t_2=1$we obtain
\[
R(q,r) = \frac{(1-q^{1/2}r)^3 (1-q^{1/2} r^{-1})^3}{(1-q)^3} .
\]
Finally, in the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.

To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
\[
I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
\eeqn
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

\parsec[s:typeAunrefinedKR]
In this section we compute the {\em unrefined} character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ where we specialize $t_1=t_2=1$.
From the long exact sequence \eqref{eqn:les1} we have the following expression 
\beqn
\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
\eeqn 
We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
\beqn
\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
\eeqn

Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
\begin{align*}
\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{-\lambda_1-j} t_2^{\lambda_1 + j} \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
%\\ 
%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
\end{align*}
and $SU(2)$ character
\begin{align*}
\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
\end{align*}

Given these formulas we see that we need to compute the sum
\begin{multline}
\sum_{j \geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{1}{1-t_1^{-1} t_2^{-1}} \sum_{j\geq 0} t^j \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
= \sum_{k=0}^{\lambda_1+j} \sum_{l=0}^k 
\end{multline}

@@

\parsec

\beqn
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \left(r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \right) .
\eeqn
Notice that 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]
so the above expression for $\ch M_j$ reduces to
\[
\ch M_j = R(r,t) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} t^j .
\]
Observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
\]
where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.

@@

In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character specializes to
\[
\ch I_A(1,0)|_{t_1=t_2=1} = \frac{r^2}{(1-t^2)^3} \left[ t^2 (r^2 + r^{-2} + 1) - 3 t (r + r^{-1}) + 3 \right] .
\]

Finally, we specialize further $t=r$ and substitute $q = t^2$ to obtain
\[
\ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
\]

>>>>

\begin{lem}
\label{lem:R}
We have
\beqn
R = \frac{1}{(1-t_1^{-1} q)(1-t_1t_2^{-1}q)(1-t_2 q)}\prod_{a=+1,-1}(1-t_1^{-1} q^{1/2} r^a)(1-t_1 t_2^{-1} q^{1/2} r^a)(1-t_2 q^{1/2} r^a)
\eeqn
\end{lem}
%which is
%\[
%0 \leftarrow I(p,0;r;\frac23 p - r) \leftarrow M(V^{p,r}) \leftarrow M(V^{p+1,r+1}) \leftarrow \cdots .
%\]

In the computations of the sections that follow we will make the substitution $q = t^2$ for notational simplicity.

\parsec[s:typeAunrefinedKR]
To obtain the formula for the character we will use a cohomological description of the irreducible modules of type $A$
\[
I_A(\lambda_1,\lambda_3) = I(\lambda_1,0,\lambda_3;\frac23 \lambda_1 - \lambda_3) .
\]
In \cite{KR2}, an exact sequence of $E(3|6)$-modules is constructed
\beqn\label{eqn:les1}
0 \leftarrow I_A(\lambda_1,\lambda_3)\leftarrow M_A(\lambda_1,\lambda_3) \leftarrow M_A(\lambda_1+1,\lambda_3+1) \leftarrow \cdots .
\eeqn 
From the long exact sequence \eqref{eqn:les1} we have the following expression for the character
\beqn
\ch I_A(\lambda_1,\lambda_3) = \sum_{j \geq 0} \ch M_A(\lambda_1+j,\lambda_3+j)  .
\eeqn 
We can apply formula \eqref{eqn:MA} to get an expression for the $j$th term
\beqn\label{eqn:chA1}
\ch M_A(\lambda_1+j,\lambda_3+j) = t^{3 \lambda_3 - 2 \lambda_1+j} R(t,r,t_1,t_2) \ch_{SU(3)}^{\lambda_1+j}(t_1,t_2) \ch_{SU(2)}^{\lambda_3+j} (r)  .
\eeqn

Applying the Weyl character formula we obtain the explicit expressions for the $SU(3)$ character
\begin{align*}
\ch_{SU(3)}^{\lambda_1+j} (t_1,t_2) & = t_1^{\lambda_1+j} t_2^{-\lambda_1 -j} \sum_{k=0}^{\lambda_1 + j} t_1^{-k} t_2^{2k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}} 
%\\ 
%& = t_1^{-2/3} t_2^{2/3} \sum_{k=0}^{\lambda_1 + j} t_1^{k/2} t_2^{-3k/2} \sum_{l = 0}^k (t_1 t_2)^l .
\end{align*}
and $SU(2)$ character
\begin{align*}
\ch_{SU(2)}^{\lambda_3+j} (r) & = r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} \\ & = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} .
\end{align*}

We proceed to evaluate the sum in \eqref{eqn:chA1}
\begin{multline}
t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1} \sum_{j \geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) R \sum_{k=0}^{\lambda_1 + j}t_1^{2k} t_2^{-k} \frac{1 - t_1^{-k-1} t_2^{-k-1}}{1-t_1^{-1} t_2^{-1}}  \\
= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \sum_{k=0}^{\lambda_1 + j} t_1^{2k} t_2^{-k} \left(1 - (t_1t_2)^{-k-1}\right) \\
= \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{1-t_1^{-1} t_2^{-1}} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \left(\frac{1 - (t_1^2 t_2^{-1})^{\lambda_1 + j + 1}}{1 - t_1^2 t_2^{-1}} - t_1^{-1} t_2^{-1} \frac{1 - (t_1 t_2^{-2})^{\lambda_1 + j + 1}}{1 - t_1 t_2^{-2}} \right) \\ =
\frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} R \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \times \\ 
\left[(1-t_1 t_2^{-2})(1-(t_1^2 t_2^{-1})^{\lambda_1+j+1}) - t_1^{-1}t_2^{-1} (1-t_1^2 t_2^{-1}) (1 - (t_1 t_2^{-2})^{\lambda_1+j+1}) \right]
%
%\\ = \frac{t^{3\lambda_3-2 \lambda_1} t_1^{-\lambda_1} t_2^{\lambda_1}}{(1-t_1^{-1} t_2^{-1})(1 - t_1^2 t_2^{-1})(1-t_1t_2^{-1})} \sum_{j\geq 0} t^j t_1^{-j} t_2^{j} \left(r^{\lambda_3+j}-r^{-\lambda_3-j-2}\right) \\ \times \left(1 + t_1^{2\lambda_1 +2j+3}t_2^{-\lambda_1-j-1} - t_1 t_2^{-2} - t_1^{2 \lambda_1 + 2j + 2} t_2^{-\lambda_1 - j -1} \right. \\ \left. - t_1^{-1} t_2^{-1} + t_1^{\lambda_1+j+2} t_2^{-2 \lambda_1 - 2j-4} + t_1 t_2^{-2} + t_1^{\lambda_1 + j} t_2^{-2\lambda_1 - 2 j - 3} \right)
\end{multline}

We split the sum $\sum_{j \geq 0}$ into four terms
\begin{itemize}
\item the first term is 
\beqn
(1-t_1t_2^{-2}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{2 \lambda_1 + j + 2} t_2^{-\lambda_1 - 1} \right) .
\eeqn
Evaluating the infinite series this becomes
\begin{multline} 
r^{\lambda_3} (1-t_1 t_2^{-2}) \left(\frac1{1-trt_1^{-1}t_2} - \frac{t_1^{2\lambda_1+2}t_2^{-\lambda_1-1}}{1 - t r t_1} \right) \\ = \frac{r^{\lambda_3}(1-t_1 t_2^{-2})}{(1-trt_1^{-1}t_2)(1 - t r t_1)} \left(1 - trt_1-t_1^{2\lambda_1+2} t_2^{-\lambda_1-1}+tr t_1^{2 \lambda_1+1} t_2^{-\lambda_2}\right)
\end{multline}
\item the second term is
\beqn
t_1^{-1} t_2^{-1}(1-t_1^2 t_2^{-1}) \sum_{j \geq 0} t^j r^{\lambda_3 + j} \left(t_1^{-j} t_2^j - t_1^{\lambda_1+1} t_2^{-2\lambda_1 - j - 2}\right) .
\eeqn
\end{itemize}

@@

\parsec
In this section we deduce an explicit formula for the character of the type $A$ modules $I_A(\lambda_1,\lambda_3)$ after specializing $t_1=t_2=1$. 
In this specialization it is easy to see that 
\[
\ch_{SU(3)}^{\lambda_1+j}(t_1=t_2=1) = \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} ,
\]
which is just the dimension of polynomials of homogenous degree $\lambda_1+j$ in three variables.

We thus arrive at the expression for the $j$th term in the sum appearing in equation \eqref{eqn:IA1}:
\beqn\label{eqn:chA1}
\ch M_A(\lambda_1+j,\lambda_3+j)_{t_1=t_2=1} = R(t,r) t^{3 \lambda_3 - 2 \lambda_1} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} t^j \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} 
\eeqn
where $R(t,r)$ is the specialization at $t_1=t_2=1$ of $R$
\[
R(t,r) = \frac{(1-tr)^3 (1-t r^{-1})^3}{(1-t^2)^3} ,
\]
which we read off readily from Lemma \ref{lem:R}
In this expression we have also utilized the $SU(2)$ character formula for the irreducible module of heighest weight $\lambda_3+j$: 
\[
r^{\lambda_3+j}+ r^{\lambda_3+j-2} + \cdots + r^{-\lambda_3-j} = \frac{r^{\lambda_3+j}-r^{-\lambda_3-j-2}}{1-r^{-2}} ,
\]

Now, observe the formal identity 
\[
\sum_{j \geq 0} \frac{(\lambda_1+j+1)(\lambda_1+j+2)}{2} x^j = \frac{p(x)}{(1-x)^3}  .
\]
where $p(x) = \frac12 \left(\lambda_1^2 x^2 + \lambda_1 x^2 - 2\lambda_1^2x -4 \lambda_1 x + \lambda_1^2 + 3\lambda_1 +2\right)$.

@@

In the case that $\lambda_1=0$ and $\lambda_3=1$ we see that this specialized character simplifies to
\beqn
\ch I_A(0,1)|_{t_1=t_2=1} = \frac{t^3(r+r^{-1}) + t^6 - 3 t^4}{(1-t^2)^3} .
\eeqn

In the case that $\lambda_1 = 1$ and $\lambda_3 = 0$ we see that this unrefined character simplifies to
\beqn
\ch I_A(1,0)|_{t_1=t_2=1} = \frac{(r^2 + r^{-2} + 1) - 3 t^{-1} (r + r^{-1}) + 3t^{-2} }{(1-t^2)^3} .
\eeqn
\brian{The $(1,0)$ character differs from $N=2$ index by a factor of $t^6 = q^3$ as expected.}

Finally, for general $\lambda_1,\lambda_3$ we specialize further $t=r$ and substitute $q = t^2$ to obtain
\beqn
\ch I_A(\lambda_1,\lambda_3) = \frac{q^{\lambda_3 - \lambda_1}}{1-q} .
\eeqn
